\ttitle

### 2015-06-02 Chapters/Introduction.tex
Added papers to read re jaundice physiology - remove these in final version.

\subsection{Impact of jaundice on cardiovascular physiology}
\subsection{Impact of jaundice on renal physiology}
\subsection{Impact of jaundice on the immune system}
\subsection{Jaundice and postoperative outcomes}
\subsection{Role of preoperative biliary drainage}

>>>>

Until recently, major surgery in jaundiced patients has been considered to be more prone to adverse postoperative events. While this concept has been recently challenged, surgeons remain wary of operating on the severely jaundiced patient. In fact, pancreaticoduodenectomy was initially described as a two-stage procedure where the first stage involved a biliary bypass aimed at relieving obstructive jaundice before the second stage of resection was carried out.

\subsection{Impact of jaundice on cardiovascular physiology}
%Read the following papers:
%yang_clinical_2010
%padillo_improved_2001
%khurana_bile_2011
%green_jaundiced_1986

\subsection{Impact of jaundice on renal physiology}

\subsection{Impact of jaundice on the immune system}
%nehez_compromise_2002 - get other citations from this one

\subsection{Jaundice and postoperative outcomes}
\subsection{Role of preoperative biliary drainage}

\section{Body Composition}
Make this a brief description of body composition.
